Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
done

The following are the performance results for the clinical data given a prior
mean for the regression parameters of $\mu=-1.6$.  The full HSLDA model had a
true positive rate of 0.57  
and a false positive rate of 0.13, the sLDA model had a true positive
rate of 0.42 and a false positive rate of 0.07, and the HSLDA model where
LDA and the regressions were fit separately had a true positive rate of 0.39
and a false positive rate of 0.08.

@@

The following are the predictive performance results for the retail product
data given a prior mean for the regression parameters of $\mu=-2.2$. 
The full HSLDA model had a true positive rate of 0.85 
and a false positive rate of 0.30, the sLDA model had a true positive
rate of 0.78 and a false positive rate of 0.14, and the HSLDA model where
LDA and the regressions were fit separately had a true positive rate of 0.77
and a false positive rate of 0.16. These results follow a similar pattern to the clinical data.

As sensitivity and specificity can always be traded off we examined sensitivity for a range of values
for two different parameters - the prior means for the regression coefficients
and the threshold for the auxiliary variables.  The goal in this analysis
was to evaluate the performance of these models subject to more or less
stringent requirements for predicting positive labels. These two parameters 
have important related functions in the model. The prior mean in combination 
with the auxiliary variable threshold together encode the strength of the prior
belief that unobserved labels are likely to be negative. Effectively, the
prior mean applies negative pressure to the predictions and the auxiliary
variable threshold determines the cutoff.

For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  This is a proper Bayesian
sensitivity analysis. In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference and the auxiliary variable threshold is varied
following inference.  However, as intended, they both highlight model performance
under more or less stringent requirements for predicting positive labels.

>>>>

Figure~\ref{fig:1a} shows the results for the clinical data. For instance, 
a prior mean for the regression of $\mu=-1.6$ yields the following performance:
the full HSLDA model had a 
true positive rate of 0.57 and a false positive rate of 0.13, the sLDA model
had a true positive rate of 0.42 and a false positive rate of 0.07, and the
HSLDA model where LDA and the regressions were fit separately had a true
positive rate of 0.39 and a false positive rate of 0.08.

@@

Figure~\ref{fig:1b} shows the results for the retail product data. For
instance, a prior mean for the regression of $\mu=-2.2$ yields the following
performance: the full HSLDA model had a true positive rate of 0.85 
and a false positive rate of 0.30, the sLDA model had a true positive
rate of 0.78 and a false positive rate of 0.14, and the HSLDA model where
LDA and the regressions were fit separately had a true positive rate of 0.77
and a false positive rate of 0.16. These results follow a similar pattern to the clinical data.

As sensitivity and specificity can always be traded off, we examined
sensitivity for a range of values for two different parameters -- the prior
means for the regression coefficients and the threshold for the auxiliary
variables.  The goal in this analysis was to evaluate the performance of these
models subject to more or less stringent requirements for predicting positive
labels. These two parameters have important related functions in the model. The
prior mean in combination with the auxiliary variable threshold together encode
the strength of the prior belief that unobserved labels are likely to be
negative. Effectively, the prior mean applies negative pressure to the
predictions and the auxiliary variable threshold determines the cutoff. 
For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  This is a proper Bayesian
sensitivity analysis. In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference and the auxiliary variable threshold is varied
following inference.
%However, as intended, they both highlight model performance 
%under more or less stringent requirements for predicting positive labels.
